Simulation Tables

### 2019-06-14 mcmc_draws_2019-06-11/tables.Rmd
simulation changes

---
title: "Paper Tables"
author: "Carter Allen"
date: "3/26/2019"
output: 
  pdf_document: 
    keep_tex: yes
---

@@

```{r}
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("Z")
```

@@

pi_est <- col_summarize(PI)
pi_true <- rep(0.33,3)

model_component <- c("MVSN","Regression","","","","","","","","","","","","","","","","","","","","",
                     "Multinom.","Logit","","","","",
                     "Clustering")
params <- c("$\\beta_{11}$","$\\beta_{12}$","$\\beta_{13}$","$\\beta_{14}$",
            "$\\beta_{21}$","$\\beta_{22}$","$\\beta_{23}$","$\\beta_{24}$",
            "$\\sigma_{11}$","$\\sigma_{12}$","$\\sigma_{13}$","$\\sigma_{14}$",
            "$\\sigma_{22}$","$\\sigma_{23}$","$\\sigma_{24}$",
            "$\\sigma_{33}$","$\\sigma_{34}$",
            "$\\sigma_{44}$",
            "$\\psi_{1}$","$\\psi_{2}$","$\\psi_{3}$","$\\psi_{4}$",
            "$\\delta_{11}$","$\\delta_{12}$","$\\delta_{21}$",
            "$\\delta_{22}$","$\\delta_{31}$","$\\delta_{32}$",
            "$\\pi_l$")

@@

t1 <- cbind(#model_component,params,
            true_c1,est_c1,
            true_c2,est_c2,
            true_c3,est_c3)
colnames(t1) <- c(# "Model Component",
                  # "Parameter",
                  "True","Est. (95\\% CrI)",
                  "True","Est. (95\\% CrI)",
                  "True","Est. (95\\% CrI)")
```

```{r}
kable(t1)
```

```{r,eval=FALSE}
kable(t1,booktabs = T,escape = F,caption = "Model results for simulated data with n = 500, k = 4, p = 2, h = 3, v = 3. 500 iterations were run with a burn in of 100. Missingness mechanism was MAR and P(miss) = 0.25.") %>%
    kable_styling(font_size = 8) %>%
    add_header_above(c(" " = 2,"Class 1" = 2, "Class 2" = 2, "Class 3" = 2)) %>%
    group_rows(" ",1,8) %>%
    group_rows(" ",9,18) %>%
    group_rows(" ",19,22) %>%
    group_rows(" ",23,28) %>%
    group_rows(" ",29,29)
```

>>>>

---
title: "Simulation Tables"
author: "Carter Allen"
date: "4/11/2019"
output: 
  pdf_document: 
    keep_tex: yes
---

@@

```{r}
load("BETA")
load("beta_true")
load("DELTA")
load("delta_true")
load("PI")
load("PSI")
load("psi_true")
load("SIGMA")
load("sig2_true")
load("pi_true")
load("Z")
```

@@

pi_est <- col_summarize(PI)
pi_true <- round(pi.true,2)

model_component <- c("MVSN","Regression","","","","","","","",
                     "Multinom.","",
                     "Clustering")
params <- c("$\\beta_{0}$","$\\beta_{1}$","$\\beta_{2}$","$\\beta_{3}$",
            "$\\sigma_{11}$","$\\sigma_{12}$",
            "$\\sigma_{22}$",
            "$\\psi_{1}$","$\\psi_{2}$",
            "$\\delta_{11}$","$\\delta_{12}$",
            "$\\pi_l$")

@@

t1 <- cbind(model_component,
            params,
            true_c1,est_c1,
            true_c2,est_c2,
            true_c3,est_c3)
colnames(t1) <- c("Model Component",
                  "Parameter",
                  "True","Est. (95\\% CrI)",
                  "True","Est. (95\\% CrI)",
                  "True","Est. (95\\% CrI)")
```

```{r}
rownames(t1) <- NULL
kable(t1, booktabs = T, escape = F,caption = "Model results for simulated data with n = 1500, k = 2, p = 2, h = 3, v = 1. 5000 iterations were run with a burn in of 1000. Missingness mechanism was MAR and P(miss) = 0") %>%
  kable_styling(font_size = 8) %>%
  add_header_above(c(" " = 2,"Class 1" = 2, "Class 2" = 2, "Class 3" = 2)) %>%
  group_rows(" ",1,4) %>%
  group_rows(" ",5,7) %>%
  group_rows(" ",8,10) %>%
  group_rows(" ",10,10) %>%
  group_rows(" ",12,12)
```

```{r,eval=FALSE}

kable(t1,booktabs = T,escape = F,caption = "Model results for simulated data with n = 500, k = 4, p = 2, h = 3, v = 3. 500 iterations were run with a burn in of 100. Missingness mechanism was MAR and P(miss) = 0.25.",
      row.names = NA) %>%
    kable_styling(font_size = 8) %>%
    add_header_above(c(" " = 2,"Class 1" = 2, "Class 2" = 2, "Class 3" = 2)) %>%
    group_rows(" ",1,4) %>%
    group_rows(" ",5,7) %>%
    group_rows(" ",8,10) %>%
    group_rows(" ",11,11) %>%
    group_rows(" ",12,12)
```
